Online Multiclass Linear Classification with Bandit Feedback

### 2018-11-28 arxiv-version/main.tex
Small fixes in the introduction

In this paper, we focus on the special case when the examples lie in $\R^d$ and
are \emph{linearly separable with a margin}. In the full-information feedback
setting, it is well know that if the examples have norm at most $R$ and are
linearly separable with a margin $\gamma$ then the \textsc{Multiclass
Perceptron} algorithm makes at most $\lfloor 2(R/\gamma)^2 \rfloor$ mistakes.
This result is very satisfactory since the upper bound on the number of mistakes
is information-theoretically optimal and at the same time the \textsc{Multiclass
Perceptron} algorithm has low time and memory complexity.

@@

Finally, we study two questions related to the computational and
information-theoretic hardness of the problem. Any algorithm for the bandit
setting collects information in the form of so called \emph{strongly labeled}
and \emph{weakly labeled} examples. Strongly-labeled examples are those for
which we know the class label. Weakly labeled example is an example for which we
know that class label can be anything except for a particular one class. First,
we show the offline problem of finding a linear multiclass separator consistent
with the strongly- and weakly-labeled examples is NP-hard. This result is a
simple consequence of the fact that finding an intersection of two halfspaces
consistent with binary-labeled examples is NP-hard~\citep{Blum-Rivest-1993}.
Second, we show that any algorithm that uses only strongly-labeled examples and
ignores weakly labeled examples makes at least $\Omega(???)$ mistakes.

>>>>

In this paper, we focus on the special case when the examples lie in $\R^d$ and
are \emph{linearly separable with a margin}. In the full-information feedback
setting, it is well know that if the examples have norm at most $R$ and are
linearly separable with a margin $\gamma$ then the \textsc{Multiclass
Perceptron} algorithm makes at most $\lfloor 2(R/\gamma)^2 \rfloor$ mistakes.
This result is very satisfying since the upper bound on the number of mistakes
is information-theoretically optimal and at the same time the \textsc{Multiclass
Perceptron} algorithm has low time and memory complexity.

@@

Finally, we study two questions related to the computational and
information-theoretic hardness of the problem. Any algorithm for the bandit
setting collects information in the form of so called \emph{strongly labeled}
and \emph{weakly labeled} examples. Strongly labeled examples are those for
which we know the class label. Weakly labeled example is an example for which we
know that class label can be anything except for a particular one class. First,
we show the offline problem of finding a linear multiclass separator consistent
with a set of strongly and weakly labeled examples is NP-hard. This result is a
consequence of the fact that finding an intersection of two halfspaces
consistent with a set of binary-labeled examples is
NP-hard~\citep{Blum-Rivest-1993}. Second, we show that any algorithm that uses
only strongly-labeled examples and ignores weakly labeled examples makes at
least $\Omega(???)$ mistakes.
